### 2013-03-30 exam6/2.tex
now it builds

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\centerline{\Large CSU2510H Exam 1 \ifrubric (SOLUTION) \fi-- Spring 2013}

@@

\noindent\begin{minipage}{8cm}\sloppy
\begin{itemize}
\item You may use the usual primitives and expression forms of any of
  the \code{class} languages; for everything else, define it.

\item You may write {\tt {\slshape c} $\rightarrow$ {\slshape e}} as
  shorthand for
  {\tt (check-expect {\slshape c e})}.

@@

\item Some basic test taking advice: Before you start answering
any problems, read \emph{every} problem, so your brain can  think
about the harder problems in the background while you knock off the easy ones.
\end{itemize}

\bigskip

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\centerline{\Large CSU2510H Exam 2 \ifrubric (SOLUTION) \fi-- Spring 2013}

@@

\noindent\begin{minipage}{8cm}\sloppy
\begin{itemize}

\item All problems must be done in Java. You may use any Java we have
  used in class and in lab; anything else must be defined.

\item You may write {\tt {\slshape c} $\rightarrow$ {\slshape e}} as
  shorthand for writing {\tt
    Tester.checkExpect}; the {\tt Examples} class and {\tt test}
  method around the tests are not required.

@@

\item Some basic test taking advice: Before you start answering
any problems, read \emph{every} problem, so your brain can  think
about the harder problems in the background while you knock off the easy ones.
\end{itemize}
\bigskip
